Tutorial: SQL-on-Hadoop Systems

### 2015-04-01 paper.tex

\documentclass{vldb}

@@

\end{document}

>>>>

<<<<<<< HEAD
\documentclass{vldb}

\numberofauthors{1}

% 1st author
\author{
}

An important aspect of SQL-on-Hadoop, which is orthogonal to all these categories, is the various HDFS file formats used to store the data. While text is an important format for in-situi SQL analysis, and ELT processing, various columnar formats have been proposed to provide fast analytics query processing. In this tutorial, we will first introduce these file formats, then we propose to describe the SQL-on-Hadoop systems in detail, examine their architectural differences, and cover in-depth their approach to indexing, updates, query optimization, as well as new algorithms they introduce in a 3-hour tutorial.

Spark is a fast general purpose cluster computing engine that is compatible with Hadoop data.  There are three different systems that use Spark as their run-time for SQL processing: Shark \cite{shark}, Hive on Spark \cite{hiveSpark}, and Spark SQL \cite{sparkSQL}. Shark replaces the MapReduce run-time of Hive \cite{hive} with Spark. It is still uses the Hive compiler, and interfaces but genereates Spark jobs. Hive on Spark is another attempt at replacing MapReduce/Tez based run-times of Hive with Spark. Spark SQL uses the Shark \cite{shark} run-time but replaces the HiveQL and compiler with SQL, and a new compiler that uses the catalyst query optimizer.

\end{document}
=======
\documentclass{vldb}

@@

\end{document}
>>>>>>> 00c35ab89251481b8a28e301eb998b70cd2800b3
